---
title: "Marlow Assignment 2"
author: "Tom Marlow"
date: "February 29, 2016"
output: html_document
---



```{r, echo= FALSE, message= FALSE, warning= FALSE}
library(readr)
library(dplyr)
library(ggplot2)
#setwd("~/Google\ Drive/event_history_analysis/EHA_assignment2/Inputs")

#read in data

df <- read_csv("Inputs/exercise_table2_2.csv")

df <- df %>%                     # this is the pipe magic function. It just passes 
  rename( a = survival_year,     # the results of the previous function to the next.
          b =numalivebint,       # Very useful for data cleaning tasks.
          c = numdeadint) %>% 
  mutate(S = b/100000, 
         f = c/(5*100000), 
         h = (c/5)/(b-(.5*c)))

df
```

### Question 1

**a**
```{r, echo = FALSE}
xlabels <- df$ageinterval # x axis labels 

survival <- ggplot(df, aes(x= interval, y = S)) + geom_step(color = "blue") +
  labs(x = "Age Interval (yrs)", y = "S(t)") + ggtitle("Survival Function") +
  scale_x_continuous(breaks=seq(1, 19, 2), labels = xlabels[seq(1,19,2)]) + theme_minimal()

survival
```

```{r, echo = FALSE}
prob_density <- ggplot(df, aes(x= interval, y = f)) + geom_line(color = "green") +
  labs(x = "Age Interval (yrs)", y = "f(t)") + ggtitle("Probability Density Function") + theme_minimal() + scale_x_continuous(breaks=seq(1, 19, 2), labels = xlabels[seq(1,19,2)])
prob_density
```

```{r, echo= FALSE}
hazard <- ggplot(df, aes(x= interval, y = h)) + geom_line(color = "red") +
  labs(x = "Age Interval (yrs)", y = "h(t)") + ggtitle("Hazard Function") + theme_minimal() +
  scale_x_continuous(breaks=seq(1, 19, 2), labels = xlabels[seq(1,19,2)])
hazard
```

```{r, echo= FALSE}
prob_haz <- ggplot(df, aes(x= interval, y = h)) + geom_line(color = "red") +
  geom_line(aes(x=interval, y = f), color = "green") + 
  labs(x = "Age Interval (yrs)", y = "h(t)") + ggtitle("Probability Density and Hazard Function") + theme_minimal() +
  scale_x_continuous(breaks=seq(1, 19, 2), labels = xlabels[seq(1,19,2)])
prob_haz
```


**1b** - Looking at the survivorship function, an estimate of the age at which half of the population survives is somewhere between 70 and 75. At the start of the interval for 70-75 years over 50 percent of the population is still alive. By the start of the interval for 75-80 years of age less that 50 percent of the population is alive. 

**1c** - The graph of the probability density function with the hazard function, indicates that about age 60, there is a divergence in these two functions. At age 60, the hazard function begins to increase rapidly compared to the change in the probability density function. Looking at the values 

2c . Median survival time at age 0 

tj = 70  ti = 0 
b = 5 (width of interval)
stj = .60 

tj + 1 = 75 

74.2 is the answer 

2d. = .94005

2f. at age 1, 2.59% of the population has failed


each time have death and censored dummy variable 